---
title: "HW1"
output: html_document
date: '2022-04-01'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Questions 

Question 1.

Supervised learning is a form of machine learning task where data consists of input and output pairs. This means that one can evaluate a model by comparing the predicted values with the true output values. However this is impossible in case of unsupervised learning where data only consists of inputs.

Question 2.

Regression model is used for data with continuous $Y$s, which means $Y$s have numerical values. On the other hand, classification model is used when $Y$s have categorical values.

Question 3.
For regression problems, Root Mean Squared Error (RMSE) and Mean Absolute Error (MAE) are commonly used. For classification problems, confusion matrix and AUC-ROC are some of the most popular metrics.

Question 4.
- Descriptive models: to find the best way to describe or summarize the characteristics of data
- Inferential models: to test theories and make generalizations about the larger population
- Predictive models: to predict and forecast future outcomes with minimum reducible error

Question 5.


Question 6.

## Exercises

```{r}
library(tidyverse)
library(ggplot2)
```

Exercise 1

```{r}
ggplot(mpg, aes(x = hwy)) + geom_histogram()
```

Exercise 2.

```{r}
ggplot(mpg, aes(x = hwy, y = cty)) + geom_point()
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

Exercise 3.

```{r}
ggplot(mpg, aes(x = manufacturer)) + geom_bar() + coord_flip()
```

Exercise 4.

```{r}
ggplot(mpg, aes(x = cyl, y = hwy)) + geom_boxplot()
```

Exercise 5.

```{r}
install.packages('corrplot')
```

```{r}
library(corrplot)
my_data <- select(mpg, displ, cyl, cty, hwy)
M = cor(my_data)
corrplot(M, type = 'lower')
```

Exercise 6.

```{r}
install.packages('ggthemes')
```

```{r}
library('ggthemes')
ggplot(mpg, aes(x = hwy, y = class)) + geom_boxplot() + labs(x = 'Highway MPG', y = 'Veichle Class') + theme_economist_white(gray_bg = FALSE)
```

Exercise 7.

```{r}
ggplot(mpg, aes(x = class, y = hwy, fill = drv)) + geom_boxplot()
```

Exercise 8.

```{r}
ggplot(mpg, aes(x = displ, y = hwy, color = drv)) + geom_point() + geom_smooth(aes(linetype = drv), color = 'blue', se = FALSE)
```
